What We Eval in the Shadows

### 2021-08-04 paper/main.tex
Add glue and withr package examples

@@

>>>>

The \c{glue} package provides functions for string interpolation; text enclosed
by c{\{} and c{\}} is evaluated using \eval as an R expression and replaced by
its result. The code snippet below shows an example of this.

\begin{lstlisting}
library(glue)
greeting <- "Hello"
glue('{greeting} World!')
#> Hello World!
\end{lstlisting}

@@

The \c{withr} package provides the \c{defer} function which defers the
evaluation of an expression until a stack frame is exited. It attaches this
expression as an attribute to the frame environment and uses \eval to evaluate
it on frame exit.
